\documentclass{book}
\usepackage{inputenc}
\usepackage{amsmath}
\setlength{\parindent}{0pt}

\title{Discrete Structures 1}
\author{Gianna Cantor}
\date{October 17, 2025}

\begin{document}

\maketitle

\chapter{Direct \& Indirect Proof}

\section{Problem I: Direct Proof}

\textbf{Statement:} \\
Prove that the concatenation of two binary strings of even length always results in a binary string of even length. \\

\textbf{Proof:} \\
Assume A and B are binary strings. \\
Let the length of A be even, and the length of B be even. \\
Then, \\
\begin{equation*}
    Length(A) = 2m \quad and \quad Length(B) = 2n
\end{equation*}
where m and n are integers. \\
Let AB denote the concatenation of A and B. \\
Then, \\
\begin{equation*}
    Length(AB) = Length(A) + Length(B)
\end{equation*}
By substitution, this follows that: \\
\begin{equation*}
\begin{split}
    Length(AB) & = 2m + 2n \\
               & = 2(m + n)
\end{split}
\end{equation*}
Since m + n is an integer, Length(AB) is divisible by 2, and therefore even. \\

\vspace{1em}
\fbox{\parbox{\linewidth}{Hence, the concatenation of two binary strings of even length always results in a binary string of even length. QED.}}

\section{Problem II: Indirect Proof}
\textbf{Statement:} \\
Prove that if a number n is the product of two odd integers, then n cannot be even. \\

\textbf{Proof:} \\
Assume a and b are odd integers. \\
Let n = ab. \\
Then, \\
\begin{equation*}
    a = 2k + 1 \quad and \quad b = 2p + 1
\end{equation*}
for some integers k and p. \\
By negation of conclusion, assume that n is even. \\
This follows that: \\
\begin{equation*}
\begin{split}
    n & = ab = (2k + 1)(2p + 1) \\
    n & = 4kp + 2k + 2p + 1 \\
    n & = 2(2kp + k + p) + 1
\end{split}
\end{equation*}
Let m = 2kp + k + p. \\
Since k and p are integers, and m is an integer, \\
\begin{equation*}
    n = 2m + 1
\end{equation*}
However, 2m + 1 represents and odd integer, and contradicts our assumption that n is even. \\

\vspace{1em}
\fbox{\parbox{\linewidth}{Hence, the product of two odd integers is odd (it cannot be even). QED.}}

\end{document}